---
title: "pi_curves_nls"
author: "Ariana S Huffmyer"
date: "3/18/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message = FALSE, warning = FALSE)
```

```{r load_packages}
## install packages if you dont already have them in your library
if ("devtools" %in% rownames(installed.packages()) == 'FALSE') install.packages('devtools') 
if ("segmented" %in% rownames(installed.packages()) == 'FALSE') install.packages('segmented') 
if ("plotrix" %in% rownames(installed.packages()) == 'FALSE') install.packages('plotrix') 
if ("gridExtra" %in% rownames(installed.packages()) == 'FALSE') install.packages('gridExtra') 
if ("LoLinR" %in% rownames(installed.packages()) == 'FALSE') install_github('colin-olito/LoLinR') 
if ("lubridate" %in% rownames(installed.packages()) == 'FALSE') install.packages('lubridate') 
if ("chron" %in% rownames(installed.packages()) == 'FALSE') install.packages('chron') 
if ("plyr" %in% rownames(installed.packages()) == 'FALSE') install.packages('plyr') 
if ("dplyr" %in% rownames(installed.packages()) == 'FALSE') install.packages('dplyr') 
if ("phytotools" %in% rownames(installed.packages()) == 'FALSE') install.packages('phytotools') 
if ("tidyverse" %in% rownames(installed.packages()) == 'FALSE') install.packages('tidyverse') 
if ("broom" %in% rownames(installed.packages()) == 'FALSE') install.packages('broom') 
if ("ggpubr" %in% rownames(installed.packages()) == 'FALSE') install.packages('ggpubr') 

#Read in required libraries

library("devtools")
library("ggplot2")
library("segmented")
library("plotrix")
library("gridExtra")
library("LoLinR")
library("lubridate")
library("chron")
library('plyr')
library('dplyr')
library('phytotools')
library("tidyverse")
library("broom")
library('ggpubr')
```

# Import data
```{r import_data}
Data <- read.csv(file = 'output/1_pi_curve_rates.csv')
#Data <- Data[1:40,]
```


# Define data  

```{r}
#specify data
Data$PAR <- as.numeric(Data$Light_Value)
Data$Pc <- as.numeric(Data$micromol.cm2.h)

Data <- Data %>% filter(!Run %in% c(4,5,6)) %>% filter(!colony_id %in% c("Mdec-D3", "Mcav-B2"))

Data %>%
ggplot(aes(x=PAR, y=Pc, color=Species))+
  geom_point()

```



# Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit
Aquatic Photosynthesis, Falkowski   
Pmax = max photosynthesis (AKA Am from Bayesian script)  
alpha = quantum yeild (AKA AQY from Bayesian script)  
I/E = irradiance (AKA PAR from Bayesian script)  
Rd = dark respiration   

Run models 

Using fixed initial values (keeping for reference):  

```{r}
# nls_data <- Data %>%
# group_by(colony_id) %>%
# nest(-colony_id) %>%
# mutate(model1 = map(data, ~
# nls(Pc ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4)) %>%
# tidy %>%
# dplyr::select(term, estimate) %>%
# spread(term, estimate))) %>%
# unnest(model1) %>%
# mutate(Ik = Am/AQY)%>%
# #unnest(data) %>%
# #group_by(colony_id)%>%
# #summarise(Am=mean(Am), AQY=mean(AQY), Rd=mean(Rd))%>%
# #mutate(timepoint="timepoint1")%>%
# write_csv(., "output/1_pi_curve_pars_NLS_fixed_inis.csv")
```

Using flexible initial values based on input data:  
```{r}
nls_data <- Data %>% 
   filter(PAR <550) %>%
   group_by(colony_id) %>%
   nest(-colony_id) %>%
   mutate(model1 = map(data, ~ 
                         nls(Pc ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=(max(.$Pc)-min(.$Pc)),  AQY=0.001, Rd=-min(.$Pc))) %>%
                              tidy %>%
                              dplyr::select(term, estimate) %>% 
                              spread(term, estimate))) %>%
  unnest(model1) %>%
  mutate(Ik = Am/AQY)%>%
  #unnest(data) %>%
  #group_by(colony_id)%>%
  #summarise(Am=mean(Am), AQY=mean(AQY), Rd=mean(Rd))%>%
  #mutate(timepoint="timepoint1")%>%
  write_csv(., "output/1_pi_curve_pars_NLS.csv")
```

Plot curve over data points.  
```{r}
augmented <- Data %>%
  filter(PAR <550) %>%
  nest(-colony_id) %>% 
  mutate(
    fit = map(data, ~ nls(Pc ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=1.7,  AQY=0.001, Rd=.4))),
    augmented = map(fit, augment),
  ) %>% 
  unnest(augmented)

augmented$ID <-augmented$colony_id
Aug <- augmented %>% separate(ID, c("Sp", "Num", "Type"))

#all colonies together
pdf("output/PI_Curve_Fit_Plots.pdf")
PI.curves <- Aug %>%
ggplot(aes(x=PAR, y=Pc, color=Sp))+
  geom_point() + 
  geom_line(aes(y=.fitted, x=PAR,group=colony_id))+
  scale_color_manual(values=c("green", "black", "cyan","orange"))+
  theme_classic()+
          labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")),
               y = expression(paste('Oxygen flux (', mu, "mol cm"^-2, 'h'^-1,")")))+
  theme(legend.position = c(0.8, 0.2))
PI.curves
dev.off()

```


# Import PI curve fitted parameters for each individual
```{r}
pars <- read_csv("output/1_pi_curve_pars_nls.csv")
```

# Import sample metadata
```{r}
md <- read_csv("data/1_pi_curves/coral_metadata.csv")

df <- left_join(pars, md)
```

# Plot data and boxplots
```{r, fig.height = 8}

df <- df %>%
  pivot_longer(cols=Am:Ik, names_to="variable")

# Facet grid for each variable
pdf("output/PI_metrics_nls.pdf")
PI.params <- df %>%
  ggplot(aes(x = species, y = value,fill=species)) +
  geom_boxplot(alpha = 0.6) +
  scale_fill_manual(values=c("green", "cyan", "black", "orange"))+
  facet_wrap(~variable, scales = "free_y") +
  geom_jitter(width = 0.1)+
  theme_classic()+
  theme(legend.position="none")+
  scale_x_discrete(labels=c("Diploria labyrinthiformis" = "Dlab", "Madracis decactis" = "Mdec",
                              "Montastraea cavernosa" = "Mcav", "Porites astreoides" = "Past"))
PI.params
dev.off()

```


# Combine Plots
```{r, fig.height = 8}

#generate a combined figure of TPCs and estimate plots
figure <- ggarrange(PI.curves , PI.params,
                    labels = c("A", "B"),
                    ncol = 2, nrow = 1,
                    heights=c(1,0.5))
figure

ggsave("output/Curves.pdf", figure, dpi=300, w=7.5, h=4, units="in")

```



