---
title: "Photosynthesis and respiration rate calculations"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

## install packages if you dont already have them in your library
if (!require("devtools")) install.packages("devtools")
if (!require("furrr")) install.packages("furrr")
if (!require("future")) install.packages("future")
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("lubridate")) install.packages("lubridate")
if (!require("cowplot")) install.packages("cowplot")
if (!require("LoLinR")) install_github('colin-olito/LoLinR') 

## load libraries
library(devtools)
library(LoLinR)
library(tidyverse)
library(lubridate)
library(cowplot)
library(broom)
library(plotrix)
library(Hmisc)
library(rTPC)
library(nls.multstart)

## libraries for parallel processing
library(future)
library(furrr)
```

## Import metadata
```{r, warning = FALSE}
path.p <- "data/1_pi_curves/" #the location of all your respirometry files 

# List data files
file.names <- list.files(path = path.p, pattern = "csv$")  # list all csv file names in the folder
file.names <- file.names[!grepl("metadata", file.names)]   # omit metadata from files to be read in as data

# Load PI curve sample metadata (i.e., which corals were in which runs)
sample.info <- read_csv(file = "data/1_pi_curves/1_pi_curves_sample_metadata.csv")

# Load PI curve run metadata (i.e., light levels and interval times for each run)
run.info <- read_csv(file = "data/1_pi_curves/1_pi_curves_run_metadata.csv")

# Join all coral and run metadata
metadata <- full_join(sample.info, run.info) %>%
  mutate(Date = as_date(as.character(Date), format = "%Y%m%d", tz = "Atlantic"))

# Select only certain columns
metadata <- metadata %>%
  select(Species, colony_id, Run, Temp.Cat, Chamber.Vol.L, Date, Start.time, Stop.time, Light_Value, Light_Level)
```


# Read in all data files
```{r, results="hide", message=FALSE}
df <- tibble(file.name = file.names) %>%
  mutate(colony_id = gsub("_.*", "", file.name),                              # Get colony_id from filename
          info = map(colony_id, ~filter(metadata, colony_id == .)),           # Get associated sample info
         data0 = map(file.name, ~read_csv(file.path(path.p, .), skip=1, col_types = cols(.default = "d", Time = "t"))))   # Get associated O2 data

# Select only Time, Value, and Temp columns from O2 data
df <- df %>%
  mutate(data0 = map(data0, ~select(., Time, Value, Temp)))%>%
  mutate(data0 = map(data0, ~(.x %>% filter(complete.cases(.))))) #remove NAs 

```

## Use the time breaks in the sample info to link O2 data with light levels
```{r, warning = FALSE}
df <- df %>%
  mutate(intervals = map2(data0, info, function(.x, .y) {
    split(.x, f = cut(as.numeric(.x$Time), breaks = as.numeric(c(.y$Start.time, last(.y$Stop.time))),
                      labels = as.character(.y$Light_Value)))})) %>%
  mutate(data = map(intervals, ~ unnest(tibble(.), .id = "Light_Value")))

```

### Thin data
```{r, fig.height = 8, fig.width = 8}
# Set thinning parameter
thin_par <- 20

# Thin data for all samples
df <- df %>%
  mutate(thin_data = map(data, ~ slice(., seq(1, nrow(.), thin_par))))

# Create plots for full dataset and thinned data
df <- df %>%
  mutate(data_plot = map2(data, colony_id, ~ ggplot(.x, aes(x = Time, y = Value)) + 
                            facet_wrap(~ as.numeric(Light_Value), scales = "free") +
                            geom_point() +
                            labs(title = .y)),
    thin_data_plot = map2(thin_data, colony_id, ~ ggplot(.x, aes(x = Time, y = Value)) + 
                            facet_wrap(~ as.numeric(Light_Value), scales = "free") +
                            geom_point() +
                            labs(title = .y)))

# Example of plots
cowplot::plot_grid(df$data_plot[[1]], df$thin_data_plot[[1]], nrow = 2,
                   labels = c("Example plot: all data", "Example plot: thinned data"))
```

#### The full or thinned data plot for any sample can be accessed like this:
```
df %>%
  filter(colony_id == "ACR-185") %>%
  pull(thin_data_plot)
```

# Fit regressions to each interval for each sample
```{r}
# Define function for fitting LoLinR regressions to be applied to all intervals for all samples
fit_reg <- function(df) {
  rankLocReg(xall = as.numeric(df$Time), yall = df$Value, 
             alpha = 0.2, method = "pc", verbose = FALSE)
}

# Setup for parallel processing
future::plan(multisession)

# Map LoLinR function onto all intervals of each sample's thinned dataset
df <- df %>%
  mutate(regs = furrr::future_map(thin_data, function(.) {       # future_map executes function in parallel
    group_by(., Light_Value) %>%
    do(rankLcRg = fit_reg(.))
  }))

## Now 'regs' contains the fitted local regressions for each interval of each sample's thinned dataset

# Define function to pull out and plot regression diagnostics
plot_rankLcRg <- function(colony_id, interval_number) {
  df %>%
    filter(colony_id == colony_id) %>%
    pluck("regs", 1, "rankLcRg", interval_number) %>%
    plot()
}
```

#### The diagnostics for any regression can be plotted by specifying a colony_id and the number of the light curve interval:
```{r}
# Define function to pull out and plot regression diagnostics
# plot_rankLcRg <- function(colony_id, interval_number) {
#   df %>%
#     filter(colony_id == colony_id) %>%
#     pluck("regs", 1, "rankLcRg", interval_number) %>%
#     plot()
# }
#THIS FUNCTION IS NOT WORKING BY COLONYID
# pdf("output/Past-D1_test.pdf")
# plot_rankLcRg("Past-D1", 1)
# plot_rankLcRg("Past-D1", 2)
# plot_rankLcRg("Past-D1", 3)
# plot_rankLcRg("Past-D1", 4)
# plot_rankLcRg("Past-D1", 5)
# plot_rankLcRg("Past-D1", 6)
# plot_rankLcRg("Past-D1", 7)
# plot_rankLcRg("Past-D1", 8)
# plot_rankLcRg("Past-D1", 9)
# plot_rankLcRg("Past-D1", 10)
# dev.off()
```

### Extract slope of best regression for each interval for each sample
```{r}
df.out <- df %>% 
  unnest(regs) %>%
  mutate(micromol.L.s = map_dbl(rankLcRg, ~ pluck(., "allRegs", "b1", 1)))

#verify sample numbers
unique(df.out[[2]])
length(unique(df.out[[2]]))

xx <- select(df.out,colony_id, Light_Value, micromol.L.s)
xx$grouping.id <- paste0(xx$colony_id, "-",xx$Light_Value)
nrow(xx)
nrow(distinct(xx))

mx <- select(metadata, Species, colony_id, Run, Chamber.Vol.L, Temp.Cat)
nrow(mx)
nrow(distinct(df))

pr <- left_join(xx, mx, by="colony_id")
length(unique(pr$colony_id))
nrow(distinct(pr))
pr <-distinct(pr)
  
# Write to output file
write.csv(pr, "output/pi_curve_extracted_rates_Raw.csv")
```


# Adjust by chamber volume, subtract blank, and normalize to surface area
```{r}

###Remove extra light step from Run 1
pr <-pr %>% filter(!Light_Value>550)
length(unique(pr$colony_id))

# Correct for chamber volume 
pr <- pr %>% mutate(micromol.s = micromol.L.s * Chamber.Vol.L)
length(unique(pr$colony_id))

# Correct for blank rates

# Get blank values -- average for each run and light value in case multiple blanks
blanks <- pr %>%
  filter(grepl("BK", colony_id)) %>%
  group_by(Temp.Cat, Light_Value) %>%
  summarise(micromol.s.blank=mean(micromol.s))%>%
  mutate(blank_id=paste0(Temp.Cat,"-",Light_Value))

### generate a key for the blank id
pr <- pr %>%
  mutate(blank_id=paste0(Temp.Cat,"-",Light_Value))
length(unique(pr$colony_id))

#plot blank values
blanks %>% ggplot(aes(x=as.numeric(Light_Value), y=micromol.s.blank,colour = as.factor(Temp.Cat)))+
  geom_point()+
  geom_line()

anova(lm(micromol.s.blank~as.factor(Light_Value)*Temp.Cat, data=blanks))
# 
# #remove redundant columns in blanks prior to merging with data
# blanks <- blanks %>%
#   select("colony_id", "Run_blank_light", "micromol.s.blank")
# 


#####
# SAMPLES ARE GETTING TRUNCATED HERE
#####
# 
pr  <- left_join(pr ,blanks,by = "blank_id")
length(unique(pr$colony_id))


#Join blank values with rest of data and subtract values from samples for same run and light value
pr <- pr %>%
  mutate(micromol.s.adj = micromol.s - micromol.s.blank) %>%
  # After correcting for blank values, remove blanks from data
  filter(!grepl("BK", colony_id))
length(unique(pr$colony_id))


# Import surface area data
sa <- read.csv("output/1_surface_area.csv")

# Join surface area with rest of data
pr <- left_join(pr, select(sa, colony_id, surface.area.cm2))
length(unique(pr$colony_id))

pr  <- dplyr::inner_join(
   pr ,
   dplyr::select(sa, -any_of(names(pr)), colony_id),
   by = "colony_id"
)
length(unique(pr$colony_id))

# Normalize rates by surface area
pr <- pr %>%
  mutate(micromol.cm2.s = micromol.s.adj / surface.area.cm2,
         micromol.cm2.h = micromol.cm2.s * 3600)
length(unique(pr$colony_id))
```

# Write extracted rates to output file
```{r}
# Select variables to write to file
pr.out <- pr %>% 
  select(Species, colony_id, Light_Value.x, Run, micromol.cm2.s, micromol.cm2.h)
length(unique(pr.out$colony_id))

# Write to output file
write.csv(pr.out, "output/pi_curve_extracted_rates.csv")
```









<!-- # Define data   -->

<!-- ```{r} -->
<!-- #specify data -->
<!-- Data <- pr.out -->
<!-- Data$PAR <- as.numeric(Data$Light_Value.x) -->
<!-- Data$Pc <- as.numeric(Data$micromol.cm2.h) -->


<!-- Data <- Data %>%  -->
<!--   filter(!Run %in% c(4,5,6)) %>%  -->
<!--   filter(!colony_id %in% c("Mdec-D3", "Mcav-B2", "Dlab-B7", "Dlab-D4", "Dlab-F6")) -->

<!-- Data %>% -->
<!-- ggplot(aes(x=PAR, y=Pc, color=Species))+ -->
<!--   geom_point() -->
<!-- ``` -->

<!-- # Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit -->
<!-- #Pc ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=(max(.$Pc)-min(.$Pc)),  AQY=0.001, Rd=-min(.$Pc)) -->
<!-- Aquatic Photosynthesis, Falkowski  -->
<!-- PAR = irradiance from 400-700nm (also called I or E) -->
<!-- PC = oxygen flux rate -->
<!-- Pmax = max photosynthesis (also called Am)   -->
<!-- alpha = quantum yeild (also called AQY)   -->
<!-- I or E or PAR = irradiance  -->
<!-- Rd = dark respiration -->
<!-- Ik (saturating irradiance) is the point at which photosynthesis reaches the max of initial slope = Am/AQY -->
<!-- Ic=(Am*Rd)/(AQY*(sqrt(Am^2-Rd^2))) -->
<!-- Equation for Ic derived from quadratic equation above. Ic = Par when Pc = 0 (x intercept). Ic = light compensation point; point at which photosynthesis is released from carbon limitation.  -->

<!-- Run nls model  -->
<!-- Using flexible initial values based on input data:  -->
<!-- ```{r} -->
<!-- nls_data <- Data %>%  -->
<!--    group_by(colony_id) %>% -->
<!--    nest(-colony_id) %>% -->
<!--    mutate(model1 = map(data, ~  -->
<!--                          nls(Pc ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=(max(.$Pc)-min(.$Pc)),  AQY=0.001, Rd=-min(.$Pc))) %>% -->
<!--                               tidy %>% -->
<!--                               dplyr::select(term, estimate) %>%  -->
<!--                               spread(term, estimate))) %>% -->
<!--   unnest(model1) %>% -->
<!--   unnest(data) %>% -->
<!--   group_by(colony_id) %>% -->
<!--   summarise(Am=mean(Am), AQY=mean(AQY), Rd=mean(Rd))%>% -->
<!--   mutate(Ik=Am/AQY)%>% -->
<!--   mutate(Ic=(Am*Rd)/(AQY*(sqrt(Am^2-Rd^2)))) -->

<!--   write_csv(nls_data, "output/pi_curve_pars_nls.csv") -->
<!-- ``` -->


<!-- Plot curve over data points.   -->
<!-- ```{r} -->
<!-- augmented <- Data %>%  -->
<!--   nest(-colony_id) %>%  -->
<!--   mutate( -->
<!--     fit = map(data, ~ nls(Pc ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))), -->
<!--     augmented = map(fit, augment), -->
<!--   ) %>%  -->
<!--   unnest(augmented) -->

<!-- #all colonies together -->
<!-- augmented %>% -->
<!--   group_by(colony_id)%>% -->
<!--   qplot(PAR, Pc, data = ., geom = 'point', colour = colony_id) + -->
<!--   geom_line(aes(y=.fitted))+ -->
<!--   theme(legend.position="none") -->

<!-- #view by certain colonies to ground truth values  -->
<!-- augmented %>% -->
<!--   group_by(colony_id)%>% -->
<!--   filter(colony_id=="ACR-139")%>% -->
<!--   qplot(PAR, Pc, data = ., geom = 'point', colour = colony_id) + -->
<!--   geom_line(aes(y=.fitted))+ -->
<!--   theme(legend.position="none") -->

<!-- #view individual plots -->
<!-- by(augmented,augmented$colony_id, function(i) { -->
<!--   ggplot(i) + -->
<!--           geom_point(aes(PAR, Pc, group=colony_id)) +  -->
<!--           geom_line(aes(y=.fitted, x=PAR)) +  -->
<!--           theme_classic()+ -->
<!--           labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")), -->
<!--                y = expression(paste('Photosynthetic rate (', mu, "mol cm"^-2, 'h'^-1,")")), -->
<!--                title = paste0("1_", augmented$colony_id)) -->
<!-- }) -->

<!-- ``` -->

<!-- PI curve fitted parameters for each individual -->
<!-- ```{r} -->
<!-- pars <- nls_data -->
<!-- md <- read_csv("data/1_pi_curves/coral_metadata.csv") -->
<!-- df <- left_join(pars, md) -->

<!-- df <- df %>% -->
<!--   pivot_longer(cols=Am:Ik, names_to="variable") -->

<!-- # Facet grid for each variable -->
<!-- jpeg("output/PI_metrics_nls.jpg") -->
<!-- PI.params <- df %>% -->
<!--   ggplot(aes(x = species, y = value,fill=species)) + -->
<!--   geom_boxplot(alpha = 0.6) + -->
<!--   scale_fill_manual(values=c("green", "cyan", "black", "orange"))+ -->
<!--   facet_wrap(~variable*Temp.Cat, scales = "free_y", nrow=4) + -->
<!--   geom_jitter(width = 0.1)+ -->
<!--   theme_classic()+ -->
<!--   theme(legend.position="none")+ -->
<!--   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ -->
<!--   scale_x_discrete(labels=c("Diploria labyrinthiformis" = "Dlab", "Madracis decactis" = "Mdec", -->
<!--                               "Montastraea cavernosa" = "Mcav", "Porites astreoides" = "Past")) -->
<!-- PI.params -->
<!-- dev.off() -->
<!-- ``` -->


<!-- Load rate data and metadata -->
<!-- ```{r, warning=FALSE, message=FALSE} -->
<!-- pars <- read_csv("output/pi_curve_pars_nls.csv") -->
<!-- md <- read_csv("data/1_pi_curves/coral_metadata.csv") -->
<!-- df <- left_join(pars, md) -->

<!-- df$Am.log10 <-log10(df$Am+1) -->
<!-- df$AQY.log10 <-log10(df$AQY+1) -->
<!-- df$Rd.log10 <-log10(df$Rd+1) -->
<!-- df$Ik.log10 <-log10(df$Ik+1) -->

<!-- # add a group name by pasting Temperature and Treatment -->
<!-- df$group <- paste0(df$species,"_", df$Temp.Cat) -->
<!-- df$id_group <- paste0(df$colony_id,"_", df$Temp.Cat) -->

<!-- df <- df %>% -->
<!--   pivot_longer(cols=Am:Ic, names_to="variable") -->
<!-- ``` -->

<!-- Visualize data  -->
<!-- ```{r, warning=FALSE, message=FALSE} -->
<!-- # Visualize data -->
<!-- r_plot<-df %>% -->
<!--     ggplot(., aes(x = Temp.Cat, y = value, colour=species)) + -->
<!--     geom_point(aes(fill=species, group=species), pch = 21, size=2, alpha=0.5) +  -->
<!--     xlab("Temperature") +  -->
<!--     facet_wrap(vars(variable), scales = "free_y", nrow = 2, strip.position = "top") + -->
<!--     theme_classic() +  -->
<!--     theme(legend.position="none", -->
<!--       axis.title=element_text(face="bold", size=16), -->
<!--       axis.text=element_text(size=12, color="black"),  -->
<!--       legend.title=element_text(face="bold", size=14),  -->
<!--       legend.text=element_text(size=12)); r_plot -->

<!-- #ggsave("output/Pmax_Scatter_withOutliers.pdf", r_plot, dpi=300, w=8, h=8, units="in") -->
<!-- ``` -->

<!-- View and remove outliers.    -->
<!-- ```{r, warning=FALSE, message=FALSE} -->
<!-- #identify outliers by Temperature and Treatment groups -->
<!-- outlier.plot <- ggbetweenstats(df,group, AQY.log10, outlier.tagging = TRUE) -->
<!-- ggsave("output/Pmax_outliersbygroup.pdf", outlier.plot, dpi=300, w=16, h=8, units="in") -->

<!-- # #set quantile values -->
<!-- # q <- c(0.25, 0.75) -->
<!-- #  -->
<!-- # # calculate quantile values by Temperature and Treatment groups -->
<!-- # Quants <- df %>% -->
<!-- #   group_by(species, Temp.Cat) %>% -->
<!-- #   summarize(quant25 = quantile(AQY.log10, probs = q[1]), -->
<!-- #             quant75 = quantile(AQY.log10, probs = q[2]), -->
<!-- #             IQRbyGroup=IQR(AQY.log10)) -->
<!-- #  -->
<!-- # # add a group name by pasting Temperature and Treatment -->
<!-- # Quants$group <-paste0(Quants$species,"_", Quants$Temp.Cat) -->
<!-- #  -->
<!-- # #Calculate Quantile upper and lower ranges  -->
<!-- # Quants$upper <-  Quants$quant75+1.5*Quants$IQRbyGroup # Upper Range   -->
<!-- # Quants$lower <- Quants$quant25-1.5*Quants$IQRbyGroup # Lower Range -->
<!-- #  -->
<!-- # #join outlier cutoffs with rate data -->
<!-- # df <- left_join(df, Quants, by=group) -->
<!-- #  -->
<!-- # #remove outliers from rates -->
<!-- # x <- df %>% -->
<!-- #   filter(AQY.log10 < upper) %>% -->
<!-- #   filter(AQY.log10 > lower) #%>% -->
<!-- #   #filter(rate < 0.125) -->
<!-- #  -->
<!-- # # Visualize data following outlier removal -->
<!-- # r_plot<-df %>% -->
<!-- #     ggplot(., aes(x = Temp.Cat, y = AQY.log10, colour=species)) + -->
<!-- #     geom_point(aes(fill=species, group=species), pch = 21, size=2, alpha=0.5) +  -->
<!-- #     xlab("Temperature") +  -->
<!-- #     #scale_fill_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+ -->
<!-- #     #scale_color_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+ -->
<!-- #     ylab(expression(bold(paste(" Log 10 Pmax (µmol ", O[2], " cm"^-2, "h"^-1, ")")))) + -->
<!-- #     theme_classic() +  -->
<!-- #     theme(legend.position="none", -->
<!-- #       axis.title=element_text(face="bold", size=16), -->
<!-- #       axis.text=element_text(size=12, color="black"),  -->
<!-- #       legend.title=element_text(face="bold", size=14),  -->
<!-- #       legend.text=element_text(size=12)); r_plot -->
<!-- #  -->
<!-- # ggsave("output/Pmax_Scatter_Outliers_Removed.pdf", r_plot, dpi=300, w=8, h=8, units="in") -->

<!-- ``` -->

<!-- # **Statistical Analysis**     -->

<!-- TPC fitting  -->
<!-- Padifeld et al **rTPC and nls.multstart: A new pipeline to fit thermal performance curves in r**   -->
<!-- https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.13585   -->

<!-- Sharpe Schoolfield 1981 model -->
<!-- Schoolfield, R. M., Sharpe, P. J. H., & Magnuson, C. E. (1981). Non-linear regression of biological temperature-dependent rate models based on absolute reaction-rate theory. Journal of theoretical biology, 88(4), 719-731. https://doi.org/10.1016/0022-5193(81)90246-0 -->

<!-- ```{r} -->

<!-- # choose model -->
<!-- get_model_names() -->
<!-- #sharpeschoolhigh_1981 -->

<!-- # get start vals -->
<!-- start_vals <- get_start_vals(df$Temp.Cat,df$AQY.log10, model_name = 'sharpeschoolhigh_1981') -->

<!-- # get limits -->
<!-- low_lims <- get_lower_lims(df$Temp.Cat,df$AQY.log10, model_name = 'sharpeschoolhigh_1981') -->
<!-- upper_lims <- get_upper_lims(df$Temp.Cat,df$AQY.log10, model_name = 'sharpeschoolhigh_1981') -->

<!-- #view values -->
<!-- start_vals -->
<!-- low_lims -->
<!-- upper_lims -->
<!-- ``` -->


<!-- Dlab CURVE FIT -->
<!-- ```{r} -->
<!-- Dlab.df <- df %>%  -->
<!--   filter(species=="Diploria labyrinthiformis") %>%  -->
<!--   filter(!id_group=="Dlab-F6_26") -->

<!-- #fit  -->
<!-- Dlab.fit <- nls_multstart(Am.log10~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28), -->
<!--                                                      data = Dlab.df, -->
<!--                                                      iter = 500, -->
<!--                                                      start_lower = start_vals - 1, -->
<!--                                                      start_upper = start_vals + 1, -->
<!--                                                      lower = low_lims, -->
<!--                                                      upper = upper_lims, -->
<!--                                                      supp_errors = 'Y') -->

<!-- Dlab.fit -->

<!-- #generate the predicted data -->
<!-- Dlab_new_data <- data.frame(temp = seq(min(Dlab.df$Temp.Cat), max(Dlab.df$Temp.Cat), 0.61)) -->
<!-- Dlab.preds <- augment(Dlab.fit, newdata = Dlab_new_data) -->

<!-- #calculate TPC parameters -->
<!-- Dlab.TCP.res <- calc_params(Dlab.fit) %>% -->
<!--   mutate_all(round, 2)   # round  -->

<!-- Dlab.TCP.res -->

<!-- ### Bootstrapping  curve fit     -->

<!-- #Resampling the original data with replacement -->

<!-- # refit model using nlsLM -->
<!-- Dlab.fit_nlsLM <- minpack.lm::nlsLM(Am.log10~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28), -->
<!--                         data = Dlab.df, -->
<!--                         start = coef(Dlab.fit), -->
<!--                         lower = low_lims, -->
<!--                         upper = upper_lims, -->
<!--                         weights = rep(1, times = nrow(Dlab.df))) -->

<!-- # bootstrap using case resampling -->
<!-- Dlab.boot1 <- Boot(Dlab.fit_nlsLM, method = 'case') -->

<!-- # look at the data -->
<!-- head(Dlab.boot1$t) -->


<!-- # create predictions of each bootstrapped model -->
<!-- Dlab.boot1_preds <- Dlab.boot1$t %>% -->
<!--   as.data.frame() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(iter = 1:n()) %>% -->
<!--   group_by_all() %>% -->
<!--   do(data.frame(temp = seq(min(Dlab.df$Temp.Cat), max(Dlab.df$Temp.Cat), length.out = 100))) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref = 28)) -->

<!-- # calculate bootstrapped confidence intervals -->
<!-- Dlab.boot1_conf_preds <- group_by(Dlab.boot1_preds, temp) %>% -->
<!--   summarise(conf_lower = quantile(pred, 0.025), -->
<!--             conf_upper = quantile(pred, 0.975)) %>% -->
<!--   ungroup() -->

<!-- # plot bootstrapped CIs -->
<!-- Dlab.CI.plot <- ggplot() + -->
<!--   #geom_line(aes(temp, .fitted), Dlab.preds, col = '#3450A3') + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), Dlab.boot1_conf_preds, fill = 'green', alpha = 0.3) + -->
<!--   geom_point(aes(Temp.Cat, Am.log10), Dlab.df, size = 2, alpha = 0.5,col = 'green') + -->
<!--   theme_bw(base_size = 12) + -->
<!--   labs(x = 'Temperature (ºC)', -->
<!--        y = 'Log 10 Pmax (µmol O2/cm2/hr)') -->
<!-- Dlab.CI.plot  -->

<!-- ``` -->

<!-- Mdec CURVE FIT -->
<!-- ```{r} -->
<!-- Mdec.df <- df %>%  -->
<!--   filter(species=="Madracis decactis") %>% -->
<!--   filter(!id_group=="Mdec-B6_26") %>% filter(!id_group=="Mdec-D7_36") -->

<!-- #fit  -->
<!-- Mdec.fit <- nls_multstart(AQY.log10~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28), -->
<!--                                                      data = Mdec.df, -->
<!--                                                      iter = 500, -->
<!--                                                      start_lower = start_vals - 1, -->
<!--                                                      start_upper = start_vals + 1, -->
<!--                                                      lower = low_lims, -->
<!--                                                      upper = upper_lims, -->
<!--                                                      supp_errors = 'Y') -->

<!-- Mdec.fit -->

<!-- #generate the predicted data -->
<!-- Mdec_new_data <- data.frame(temp = seq(min(Mdec.df$Temp.Cat), max(Mdec.df$Temp.Cat), 0.6)) -->
<!-- Mdec.preds <- augment(Mdec.fit, newdata = Mdec_new_data) -->

<!-- #calculate TPC parameters -->
<!-- Mdec.TCP.res <- calc_params(Mdec.fit) %>% -->
<!--   mutate_all(round, 2)   # round  -->

<!-- Mdec.TCP.res -->

<!-- ### Bootstrapping  curve fit     -->

<!-- #Resampling the original data with replacement -->

<!-- # refit model using nlsLM -->
<!-- Mdec.fit_nlsLM <- minpack.lm::nlsLM(AQY.log10~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28), -->
<!--                         data = Mdec.df, -->
<!--                         start = coef(Mdec.fit), -->
<!--                         lower = low_lims, -->
<!--                         upper = upper_lims, -->
<!--                         weights = rep(1, times = nrow(Mdec.df))) -->

<!-- # bootstrap using case resampling -->
<!-- Mdec.boot1 <- Boot(Mdec.fit_nlsLM, method = 'case') -->

<!-- # look at the data -->
<!-- head(Mdec.boot1$t) -->


<!-- # create predictions of each bootstrapped model -->
<!-- Mdec.boot1_preds <- Mdec.boot1$t %>% -->
<!--   as.data.frame() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(iter = 1:n()) %>% -->
<!--   group_by_all() %>% -->
<!--   do(data.frame(temp = seq(min(Mdec.df$Temp.Cat), max(Mdec.df$Temp.Cat), length.out = 100))) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref = 28)) -->

<!-- # calculate bootstrapped confidence intervals -->
<!-- Mdec.boot1_conf_preds <- group_by(Mdec.boot1_preds, temp) %>% -->
<!--   summarise(conf_lower = quantile(pred, 0.025), -->
<!--             conf_upper = quantile(pred, 0.975)) %>% -->
<!--   ungroup() -->

<!-- # plot bootstrapped CIs -->
<!-- Mdec.CI.plot <- ggplot() + -->
<!--   #geom_line(aes(temp, .fitted), Mdec.preds, col = '#3450A3') + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), Mdec.boot1_conf_preds, fill = 'cyan', alpha = 0.3) + -->
<!--   geom_point(aes(Temp.Cat, AQY.log10), Mdec.df, size = 2, alpha = 0.5,col = 'cyan') + -->
<!--   theme_bw(base_size = 12) + -->
<!--   labs(x = 'Temperature (ºC)', -->
<!--        y = 'Log 10 Pmax (µmol O2/cm2/hr)') -->
<!-- Mdec.CI.plot  -->

<!-- ``` -->

<!-- Mcav CURVE FIT -->
<!-- ```{r} -->
<!-- Mcav.df <- df %>%  -->
<!--   filter(species=="Montastraea cavernosa")%>% -->
<!--   filter(!id_group=="Mcav-D7_36") -->

<!-- #fit  -->
<!-- Mcav.fit <- nls_multstart(AQY.log10~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28), -->
<!--                                                      data = Mcav.df, -->
<!--                                                      iter = 500, -->
<!--                                                      start_lower = start_vals - 1, -->
<!--                                                      start_upper = start_vals + 1, -->
<!--                                                      lower = low_lims, -->
<!--                                                      upper = upper_lims, -->
<!--                                                      supp_errors = 'Y') -->

<!-- Mcav.fit -->

<!-- #generate the predicted data -->
<!-- Mcav_new_data <- data.frame(temp = seq(min(Mcav.df$Temp.Cat), max(Mcav.df$Temp.Cat), 0.6)) -->
<!-- Mcav.preds <- augment(Mcav.fit, newdata = Mcav_new_data) -->

<!-- #calculate TPC parameters -->
<!-- Mcav.TCP.res <- calc_params(Mcav.fit) %>% -->
<!--   mutate_all(round, 2)   # round  -->

<!-- Mcav.TCP.res -->

<!-- ### Bootstrapping  curve fit     -->

<!-- #Resampling the original data with replacement -->

<!-- # refit model using nlsLM -->
<!-- Mcav.fit_nlsLM <- minpack.lm::nlsLM(AQY.log10~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28), -->
<!--                         data = Mcav.df, -->
<!--                         start = coef(Mcav.fit), -->
<!--                         lower = low_lims, -->
<!--                         upper = upper_lims, -->
<!--                         weights = rep(1, times = nrow(Mcav.df))) -->

<!-- # bootstrap using case resampling -->
<!-- Mcav.boot1 <- Boot(Mcav.fit_nlsLM, method = 'case') -->

<!-- # look at the data -->
<!-- head(Mcav.boot1$t) -->


<!-- # create predictions of each bootstrapped model -->
<!-- Mcav.boot1_preds <- Mcav.boot1$t %>% -->
<!--   as.data.frame() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(iter = 1:n()) %>% -->
<!--   group_by_all() %>% -->
<!--   do(data.frame(temp = seq(min(Mcav.df$Temp.Cat), max(Mcav.df$Temp.Cat), length.out = 100))) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref = 28)) -->

<!-- # calculate bootstrapped confidence intervals -->
<!-- Mcav.boot1_conf_preds <- group_by(Mcav.boot1_preds, temp) %>% -->
<!--   summarise(conf_lower = quantile(pred, 0.025), -->
<!--             conf_upper = quantile(pred, 0.975)) %>% -->
<!--   ungroup() -->

<!-- # plot bootstrapped CIs -->
<!-- Mcav.CI.plot <- ggplot() + -->
<!--   #geom_line(aes(temp, .fitted), Mcav.preds, col = '#3450A3') + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), Mcav.boot1_conf_preds, fill = 'black', alpha = 0.3) + -->
<!--   geom_point(aes(Temp.Cat, AQY.log10), Mcav.df, size = 2, alpha = 0.5,col = 'black') + -->
<!--   theme_bw(base_size = 12) + -->
<!--   labs(x = 'Temperature (ºC)', -->
<!--        y = 'Log 10 Pmax (µmol O2/cm2/hr)') -->
<!-- Mcav.CI.plot  -->

<!-- ``` -->


<!-- Past CURVE FIT -->
<!-- ```{r} -->
<!-- Past.df <- df %>%  -->
<!--   filter(species=="Porites astreoides") %>% -->
<!--   filter(!id_group=="Past-C6_26") %>% -->
<!--   filter(!id_group=="Past-E7_36") -->

<!-- #fit  -->
<!-- Past.fit <- nls_multstart(AQY.log10~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28), -->
<!--                                                      data = Past.df, -->
<!--                                                      iter = 500, -->
<!--                                                      start_lower = start_vals - 1, -->
<!--                                                      start_upper = start_vals + 1, -->
<!--                                                      lower = low_lims, -->
<!--                                                      upper = upper_lims, -->
<!--                                                      supp_errors = 'Y') -->

<!-- Past.fit -->

<!-- #generate the predicted data -->
<!-- Past_new_data <- data.frame(temp = seq(min(Past.df$Temp.Cat), max(Past.df$Temp.Cat), 0.7)) -->
<!-- Past.preds <- augment(Past.fit, newdata = Past_new_data) -->

<!-- #calculate TPC parameters -->
<!-- Past.TCP.res <- calc_params(Past.fit) %>% -->
<!--   mutate_all(round, 2)   # round  -->

<!-- Past.TCP.res -->

<!-- ### Bootstrapping  curve fit     -->

<!-- #Resampling the original data with replacement -->

<!-- # refit model using nlsLM -->
<!-- Past.fit_nlsLM <- minpack.lm::nlsLM(AQY.log10~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28), -->
<!--                         data = Past.df, -->
<!--                         start = coef(Past.fit), -->
<!--                         lower = low_lims, -->
<!--                         upper = upper_lims, -->
<!--                         weights = rep(1, times = nrow(Past.df))) -->

<!-- # bootstrap using case resampling -->
<!-- Past.boot1 <- Boot(Past.fit_nlsLM, method = 'case') -->

<!-- # look at the data -->
<!-- head(Past.boot1$t) -->


<!-- # create predictions of each bootstrapped model -->
<!-- Past.boot1_preds <- Past.boot1$t %>% -->
<!--   as.data.frame() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(iter = 1:n()) %>% -->
<!--   group_by_all() %>% -->
<!--   do(data.frame(temp = seq(min(Past.df$Temp.Cat), max(Past.df$Temp.Cat), length.out = 100))) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref = 28)) -->

<!-- # calculate bootstrapped confidence intervals -->
<!-- Past.boot1_conf_preds <- group_by(Past.boot1_preds, temp) %>% -->
<!--   summarise(conf_lower = quantile(pred, 0.025), -->
<!--             conf_upper = quantile(pred, 0.975)) %>% -->
<!--   ungroup() -->

<!-- # plot bootstrapped CIs -->
<!-- Past.CI.plot <- ggplot() + -->
<!--   #geom_line(aes(temp, .fitted), Past.preds, col = '#3450A3') + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), Past.boot1_conf_preds, fill = 'orange', alpha = 0.3) + -->
<!--   geom_point(aes(Temp.Cat, AQY.log10), Past.df, size = 2, alpha = 0.5,col = 'orange') + -->
<!--   theme_bw(base_size = 12) + -->
<!--   labs(x = 'Temperature (ºC)', -->
<!--        y = 'Log 10 Pmax (µmol O2/cm2/hr)') -->
<!-- Past.CI.plot  -->

<!-- ``` -->

<!-- ```{r} -->
<!--  #set plot colors -->
<!-- cols <- c("Dlab"="green",  -->
<!-- "Mdec"="cyan", -->
<!-- "Mcav"="black", -->
<!-- "Past"="orange") -->

<!-- # plot data and model fit -->
<!-- TPC.plot <- ggplot(data=df, aes()) + -->
<!--    geom_point(aes(Temp.Cat, AQY.log10), color="green", Dlab.df, size = 2, alpha = 0.5) + -->
<!--    geom_point(aes(Temp.Cat, AQY.log10), color="cyan", Mdec.df, size = 2, alpha = 0.5) + -->
<!--    geom_point(aes(Temp.Cat, AQY.log10), color="black", Mcav.df, size = 2, alpha = 0.5) + -->
<!--    geom_point(aes(Temp.Cat, AQY.log10), color="orange", Past.df, size = 2, alpha = 0.5) + -->
<!--    geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), Dlab.boot1_conf_preds, fill = "green", alpha = 0.3) + -->
<!--    geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), Mdec.boot1_conf_preds, fill = 'cyan', alpha = 0.3) + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), Mcav.boot1_conf_preds, fill = 'black', alpha = 0.3) + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), Past.boot1_conf_preds, fill = 'orange', alpha = 0.3) + -->
<!--    xlim(15.5,40.5)+ -->
<!--    scale_x_continuous(breaks=c(16,18,20,22,24,26,28,30,32,34,36,38,40))+ -->
<!--    theme_bw(base_size = 12) + -->
<!--    scale_colour_manual(name="Species",values=cols)+ -->
<!--    theme(legend.position = "top", -->
<!--          panel.border = element_blank(), panel.grid.major = element_blank(), -->
<!--          panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ -->
<!--    labs(x = 'Temperature (ºC)', -->
<!--         y = expression("Log 10 Rdark µmol Oxygen"~cm^{-2}~h^{-1})) -->

<!-- TPC.plot  -->

<!-- ggsave("output/TPC_SharpSchool.pdf", TPC.plot, dpi=300, w=8, h=8, units="in") -->

<!-- ``` -->















<!-- ### Bootstrapping curve fit    -->
<!-- Resampling the original data with replacement -->
<!-- ```{r} -->
<!-- # refit model using nlsLM -->
<!-- high.fit_nlsLM <- minpack.lm::nlsLM(rate~sharpeschoolhigh_1981(temp = temp, r_tref,e,eh,th, tref = 28), -->
<!--                         data = d.high, -->
<!--                         start = coef(high.fit), -->
<!--                         lower = low_lims, -->
<!--                         upper = upper_lims, -->
<!--                         weights = rep(1, times = nrow(d.high))) -->

<!-- # bootstrap using case resampling -->
<!-- high.boot1 <- Boot(high.fit_nlsLM, method = 'case') -->

<!-- # look at the data -->
<!-- head(high.boot1$t) -->

<!-- # create predictions of each bootstrapped model -->
<!-- high.boot1_preds <- high.boot1$t %>% -->
<!--   as.data.frame() %>% -->
<!--   drop_na() %>% -->
<!--   mutate(iter = 1:n()) %>% -->
<!--   group_by_all() %>% -->
<!--   do(data.frame(temp = seq(min(d.high$temp), max(d.high$temp), length.out = 100))) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(pred = sharpeschoolhigh_1981(temp, r_tref, e, eh, th, tref = 28)) -->

<!-- # calculate bootstrapped confidence intervals -->
<!-- high.boot1_conf_preds <- group_by(high.boot1_preds, temp) %>% -->
<!--   summarise(conf_lower = quantile(pred, 0.025), -->
<!--             conf_upper = quantile(pred, 0.975)) %>% -->
<!--   ungroup() -->

<!-- # plot bootstrapped CIs -->
<!-- high.CI.plot <- ggplot() + -->
<!--   geom_line(aes(temp, .fitted), high.preds, col = "#E9A33D") + -->
<!--   geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), high.boot1_conf_preds, fill = '#E9A33D', alpha = 0.3) + -->
<!--   geom_point(aes(temp, rate), d.high, size = 2, alpha = 0.5,col = "#E9A33D") + -->
<!--   theme_bw(base_size = 12) + -->
<!--   labs(x = 'Temperature (ºC)', -->
<!--        y = 'Respiration Rate (µmol O2/larva/min') -->
<!-- high.CI.plot -->

<!-- ``` -->

<!-- ```{r} -->
<!--  #set plot colors -->
<!-- cols <- c("ambient"="#3450A3", "high"="#E9A33D") -->

<!-- # plot data and model fit -->
<!-- TPC.plot <- ggplot(data=df, aes(x=temp)) + -->
<!--    geom_point(aes(temp, rate, color="ambient"), d.amb, size = 2, alpha = 0.5) + -->
<!--    geom_point(aes(temp, rate, color="high"), d.high, size = 2, alpha = 0.5) + -->
<!--    geom_line(aes(temp, .fitted), amb.preds, col = '#3450A3', size=2) + -->
<!--    geom_line(aes(temp, .fitted), high.preds, col = "#E9A33D", size=2) + -->
<!--    geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), high.boot1_conf_preds, fill = "#E9A33D", alpha = 0.3) + -->
<!--    geom_ribbon(aes(temp, ymin = conf_lower, ymax = conf_upper), amb.boot1_conf_preds, fill = '#3450A3', alpha = 0.3) + -->
<!--    xlim(21,33)+ -->
<!--    scale_x_continuous(breaks=c(22,24,26,28,30,32,34,36))+ -->
<!--    theme_bw(base_size = 12) + -->
<!--    scale_colour_manual(name="Treatment",values=cols)+ -->
<!--    theme(legend.position = c(0.55, 0.9), -->
<!--          panel.border = element_blank(), panel.grid.major = element_blank(), -->
<!--          panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ -->
<!--    labs(x = 'Temperature (ºC)', -->
<!--         y = expression("Respiration Rate"~µmol~O[2] ~larva^{-1}~min^{-1})) -->

<!-- TPC.plot  -->

<!-- ggsave("Pacu2021/Figures/Respiration/TPC/TPC_SharpSchool.pdf", TPC.plot, dpi=300, w=8, h=8, units="in") -->

<!-- ``` -->

<!-- ### Confidence intervals of TPC parameters    -->

<!-- ```{r} -->
<!-- broom::tidy(amb.fit_nlsLM) -->
<!-- broom::tidy(high.fit_nlsLM) -->

<!-- #AMBIENT -->
<!-- #calculate all the TPC parameters -->
<!-- amb.extra_params <- calc_params(amb.fit_nlsLM) %>% -->
<!--   pivot_longer(everything(), names_to =  'param', values_to = 'estimate') -->

<!-- #calculate CIs for all the TPC parameters -->
<!-- amb.ci_extra_params <- Boot(amb.fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(amb.fit_nlsLM)), R = 200, method = 'case') %>% -->
<!--   confint(., method = 'bca') %>% -->
<!--   as.data.frame() %>% -->
<!--   rename(conf_lower = 1, conf_upper = 2) %>% -->
<!--   rownames_to_column(., var = 'param') %>% -->
<!--   mutate(method = 'case bootstrap') -->

<!-- #join the parameters and CIs   -->
<!-- amb.ci_extra_params <- left_join(amb.ci_extra_params, amb.extra_params) -->
<!-- amb.ci_extra_params$Treatment <- "Ambient" -->

<!-- #HIGH -->
<!-- #calculate all the TPC parameters -->
<!-- high.extra_params <- calc_params(high.fit_nlsLM) %>% -->
<!--   pivot_longer(everything(), names_to =  'param', values_to = 'estimate') -->

<!-- #calculate CIs for all the TPC parameters -->
<!-- high.ci_extra_params <- Boot(high.fit_nlsLM, f = function(x){unlist(calc_params(x))}, labels = names(calc_params(high.fit_nlsLM)), R = 200, method = 'case') %>% -->
<!--   confint(., method = 'bca') %>% -->
<!--   as.data.frame() %>% -->
<!--   rename(conf_lower = 1, conf_upper = 2) %>% -->
<!--   rownames_to_column(., var = 'param') %>% -->
<!--   mutate(method = 'case bootstrap') -->

<!-- #join the parameters and CIs   -->
<!-- high.ci_extra_params <- left_join(high.ci_extra_params, high.extra_params) -->
<!-- high.ci_extra_params$Treatment <- "High" -->

<!-- #Join Ambient and High estimates and CIs -->
<!-- All_params <- rbind(amb.ci_extra_params, high.ci_extra_params) -->
<!-- All_params <- All_params %>%  -->
<!--  mutate_if(is.numeric, round, 2) -->

<!-- #Plot all of the estimates -->
<!-- estimate.plots <- ggplot(All_params, aes(Treatment, estimate, color=Treatment)) + -->
<!--   geom_point(size = 2) + -->
<!--   scale_color_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+ -->
<!--   geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) + -->
<!--   theme_bw() + -->
<!--   facet_wrap(~param, scales = 'free_y') + -->
<!--   scale_x_discrete('') -->

<!-- estimate.plots -->

<!-- #filter to only the most relavent and well characterized parameters -->
<!-- All_params <- All_params %>%  -->
<!--   filter(!param=="ctmin") %>% -->
<!--   filter(!param=="ctmax") %>% -->
<!--   filter(!param=="skewness") %>% -->
<!--   filter(!param=="thermal_safety_margin") %>% -->
<!--   filter(!param=="thermal_tolerance") %>% -->
<!--   filter(!param=="q10")%>% -->
<!--   filter(!param=="breadth") -->

<!-- #view estimate plots -->
<!-- estimate.plots <- ggplot(All_params, aes(Treatment, estimate, color=Treatment)) + -->
<!--   geom_point(size = 2) + -->
<!--   scale_color_manual(name="Treatment", values=c("#3450A3","#E9A33D"))+ -->
<!--   geom_linerange(aes(ymin = conf_lower, ymax = conf_upper)) + -->
<!--   theme_bw() + -->
<!--   labs(y = NULL)+ -->
<!--   theme(axis.title.x=element_blank(), -->
<!--         axis.text.x=element_blank(), -->
<!--         legend.position = "none", -->
<!--         strip.background = element_blank(),  -->
<!--         strip.placement = "outside") + -->
<!--   facet_wrap(~param, scales = 'free_y', nrow=1,  -->
<!--              labeller = as_labeller(c(e = "e (Energy)", eh = " eh (Energy)", rmax= "Rmax (~µmol~O[2] ~larva^{-1}~min^{-1})",topt="Topt (Temperature °C)")), strip.position = "left") + -->
<!--   scale_x_discrete('') -->

<!-- estimate.plots -->

<!-- ggsave("Pacu2021/Figures/Respiration/TPC/TPC_estimates_SharpSchool.pdf", estimate.plots, dpi=300, w=6, h=2, units="in") -->
<!-- ```  -->


<!-- ```{r} -->
<!-- #generate a combined figure of TPCs and estimate plots -->
<!-- figure <- ggarrange(TPC.plot , estimate.plots, -->
<!--                     labels = c("A", "B"), -->
<!--                     ncol = 1, nrow = 2, -->
<!--                     heights=c(1,0.5)) -->
<!-- figure -->

<!-- ggsave("Pacu2021/Figures/Figure5_TPC_estimates_SharpeSchoolfield.pdf", figure, dpi=300, w=6, h=8, units="in") -->
<!-- ggsave("Pacu2021/Figures/Figure5_TPC_estimates_SharpeSchoolfield.jpg", figure, dpi=300, w=6, h=8, units="in") -->

<!-- ```  -->

